Matroids \& testing in families of dependent hypotheses

### 2013-08-20 presentation/presentation.tex
incorporated willis comments

\item Flats are maximally dependent sets \ie $j \nsim I \forall j \in
  S\setminus I$
\item The flats of a matroid are closed under intersection
\item $S$ (global null hypothesis) is a flat
\item Every single element of $S$ (elementary hypothesis) is a flat
\item For each $I \subseteq S$, the $H_I$ as a subset of the parameter
  space is identical to the intersection hypotheses defined by it
  closure $H_{\sigma I}$ (\ie flats correspond to weakly exhaustive
  sets \cite{bergmann1988improvements})
\item Define a stepwise procedure on the flats of $M$
\end{itemize} % ends low level
\end{frame}

@@

\begin{block}{Theorem}
 Assume that $M(\mathscr{H})$ neither contains loops nor
 parallels. Assume that hypotheses $H_1$ through $H_r$ have been
 rejected. Consider that hypotheses $H_{r+1}$ through $H_{r+t}$ are
 to be tested at level $\alpha_r$ according to a prefixed order.  If
 for some $1 \leq s \leq t$ holds
 \begin{equation}
   \label{eq:cond.hierarchical}
   \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{(r+l),(r+k)\},
 \end{equation}
 hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
 at full level $\alpha_ra$.
\end{block}

@@

\begin{enumerate}
\item Pretest using consonant weighted closed test procedure (\eg
  graphical approach), let $R = \{i \in S: H_i \textrm{ rejected by pretest}\}$
\item Compute all matroid hyperplanes $\mathscr{L}$ for the matroid
  restricted to the remaining hypotheses $I$
\item $R \gets R \cup \{i: p_i \leq \min\{ w(J)_{i}\alpha: J \in
  \mathscr{L} \} \}$
\item $A \gets \{\bigcup J: \min\{p_j / w(J)_{j}: j \in J\} > \alpha,
J \in \mathscr{L} \}$
\item $I \gets I \setminus R$
\item Compute hyperplanes of next smaller rank: $\mathscr{L} \gets \{J\in \mathscr{L}: \rho J = \rho
 \mathscr{L} - 1\}$
\item Remove interval of rejected hypotheses: $\mathscr{L} \gets \{J \in \mathscr{L}: J \cap R = \emptyset\}$
\item Reduce to interval of not accepted: $\mathscr{L} \gets \{J \in \mathscr{L}: L \nsubseteq A\}$
\item Repeat until $\rho \mathscr{L} = 0$
\item Reject $R$ and $I \setminus A$
\end{enumerate}
\end{frame}
\section{Matriods from general families of hypotheses}

\begin{frame}
\frametitle{General Results}
\begin{itemize}
\item We give sufficient necessary conditions for a general family of
  hypotheses $\mathscr{H}$ to define a matroid
\item Systems with one sided hypotheses, and parallel hypotheses (\eg
 combined non-inferiority/superiority) do not give matroids with
 $\mathscr{L}$ all strictly exhaustive
\item It is an open question under which conditions the set of
  strictly exhaustive sets is given by the flats of a matroid
\end{itemize}

@@

\begin{frame}
 \frametitle{One sided hypotheses}
 \begin{block}{One-sided linear contrast hypotheses}
   A family of {\em one sided linear contrast hypotheses} is defined
   by a contrast matrix $\bs{A} \in \mathbb{R}^{m\times n}$ and
   vector $\bs{b} \in \mathbb{R}^n$ that define a  family of null
   hypotheses of the form $\mathscr{H} = \{H_i: \bs{A_i}^t\bs{\mu}
   \leq b_i,i \in \{1,...,n\}\}$, where $\bs{A}_i$ denotes the $i$-th
   column of $\bs{A}$ and $b_i$ the $i$-th componenth of $\bs{b}$.
 \end{block}
\end{frame}

>>>>

\item Flats are maximally dependent sets \ie $j \nsim I$ $\forall j \in
  S\setminus I$
\item The flats of a matroid are closed under intersection
\item $S$ (global null hypothesis) is a flat
\item Every single element of $S$ (elementary hypothesis) is a flat
\item For each $I \subseteq S$, the $H_I$ as a subset of the parameter
  space is identical to the intersection hypotheses defined by it
  closure $H_{\sigma I}$ (\ie flats correspond to weakly exhaustive
  sets \cite{bergmann1988improvements})
%\item Define a stepwise procedure on the flats of $M$
\end{itemize} % ends low level
\end{frame}

@@

\begin{block}{Theorem}
 Assume that $M(\mathscr{H})$ neither contains loops nor
 parallels. Assume that hypotheses $H_1$ through $H_r$ have been
 rejected. Consider that hypotheses $H_{r+1}$ through $H_{r+t}$ are
 to be tested at level $\alpha_r$ according to a prefixed order.  If
 for some $1 \leq s \leq t$ holds
 \begin{equation}
   \label{eq:cond.hierarchical}
   \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{(r+l),(r+k)\},
 \end{equation}
 hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
 at full level $\alpha_r$.
\end{block}

@@

\begin{enumerate}
\item Pretest using consonant weighted closed test procedure (\eg
  graphical approach), let $R = \{i \in S: H_i \textrm{ rejected by pretest}\}$
\item Compute all matroid hyperplanes $\mathscr{L}$ for the matroid
  restricted to the remaining hypotheses $I$
\item $R \gets R \cup \{i: p_i \leq \min\{ w(J)_{i}\alpha: J \in
  \mathscr{L} \} \}$
\item $A \gets \{\bigcup J: \forall j \in J,\, p_j > w(J)_{j}\alpha, J \in \mathscr{L} \}$
\item $I \gets I \setminus R$
\item Compute hyperplanes of next smaller rank: $\mathscr{L} \gets \{J\in \mathscr{L}: \rho J = \rho
 \mathscr{L} - 1\}$
\item Remove interval of rejected hypotheses: $\mathscr{L} \gets \{J \in \mathscr{L}: J \cap R = \emptyset\}$
\item Reduce to interval of not accepted: $\mathscr{L} \gets \{J \in \mathscr{L}: J \nsubseteq A\}$
\item Repeat until $\rho \mathscr{L} = 0$
\item Reject $R$ and $I \setminus A$
\end{enumerate}
\end{frame}
\section{Matriods from general families of hypotheses}

\begin{frame}
\frametitle{General Results}
\begin{itemize}
\item We give sufficient necessary conditions for a general family of
  hypotheses $\mathscr{H}$ to define a matroid
\item Systems with one-sided hypotheses, and parallel hypotheses (\eg
 combined non-inferiority/superiority) do not give matroids with
 $\mathscr{L}$ all strictly exhaustive
\item It is an open question under which conditions the set of
  strictly exhaustive sets is given by the flats of a matroid
\end{itemize}

@@

\begin{frame}
 \frametitle{One-sided hypotheses}
 \begin{block}{One-sided linear contrast hypotheses}
   A family of {\em one-sided linear contrast hypotheses} is defined
   by a contrast matrix $\bs{A} \in \mathbb{R}^{m\times n}$ and
   vector $\bs{b} \in \mathbb{R}^n$ that define a  family of null
   hypotheses of the form $\mathscr{H} = \{H_i: \bs{A_i}^t\bs{\mu}
   \leq b_i,i \in \{1,...,n\}\}$, where $\bs{A}_i$ denotes the $i$-th
   column of $\bs{A}$ and $b_i$ the $i$-th componenth of $\bs{b}$.
 \end{block}
\end{frame}
